\documentclass[11pt]{report}
\def\bl{\mbox{}\newline\mbox{}\newline{}}
\usepackage{ifthen}
\newcommand{\hide}[2]{
\ifthenelse{\equal{#1}{inherited}}%
{}%
{}%
}
\newcommand{\entityintro}[3]{%
  \hbox to \hsize{%
    \vbox{%
      \hbox to .2in{}%
    }%
    {\bf #1}%
    \dotfill\pageref{#2}%
  }
  \makebox[\hsize]{%
    \parbox{.4in}{}%
    \parbox[l]{5in}{%
      \vspace{1mm}\it%
      #3%
      \vspace{1mm}%
    }%
  }%
}
\newcommand{\isep}[0]{%
\setlength{\itemsep}{-.4ex}
}
\newcommand{\sld}[0]{%
\setlength{\topsep}{0em}
\setlength{\partopsep}{0em}
\setlength{\parskip}{0em}
\setlength{\parsep}{-1em}
}
\newcommand{\headref}[3]{%
\ifthenelse{#1 = 1}{%
\addcontentsline{toc}{section}{\hspace{\qquad}\protect\numberline{}{#3}}%
}{}%
\ifthenelse{#1 = 2}{%
\addcontentsline{toc}{subsection}{\hspace{\qquad}\protect\numerline{}{#3}}%
}{}%
\ifthenelse{#1 = 3}{%
\addcontentsline{toc}{subsubsection}{\hspace{\qquad}\protect\numerline{}{#3}}%
}{}%
\label{#3}%
\makebox[\textwidth][l]{#2 #3}%
}%
\newcommand{\membername}[1]{{\it #1}\linebreak}
\newcommand{\divideents}[1]{\vskip -1em\indent\rule{2in}{.5mm}}
\newcommand{\refdefined}[1]{
\expandafter\ifx\csname r@#1\endcsname\relax
\relax\else
{$($ in \ref{#1}, page \pageref{#1}$)$}
\fi}
\newcommand{\startsection}[4]{
\gdef\classname{#2}
\subsection{\label{#3}{\bf {\sc #1} #2}}{
\rule[1em]{\hsize}{4pt}\vskip -1em
\vskip .1in 
#4
}%
}
\newcommand{\startsubsubsection}[2]{
\subsubsection{\sc #1}{%
\rule[1em]{\hsize}{2pt}%
#2}
}
\usepackage{color}
\date{20130502}
\pagestyle{myheadings}
\addtocontents{toc}{\protect\def\protect\packagename{}}
\addtocontents{toc}{\protect\def\protect\classname{}}
\markboth{\protect\packagename -- \protect\classname}{\protect\packagename -- \protect\classname}
\oddsidemargin 0in
\evensidemargin 0in
% \topmargin -.8in
\chardef\bslash=`\\
\textheight 9.4in
\textwidth 6.5in
\title{SimJ-Basic}
\author{Software Engineering Group}
\begin{document}
\maketitle
\sloppy
\raggedright
\tableofcontents
\gdef\packagename{}
\gdef\classname{}
\newpage
\def\packagename{fabrique}
\chapter{\bf Package fabrique}{
\vskip -.25in
\hbox to \hsize{\it Package Contents\hfil Page}
\rule{\hsize}{.7mm}
\vskip .13in
\hbox{\bf Classes}
\entityintro{EvenementNouvelleMachine}{l0}{This class implements the creation of a new machine event.}
\entityintro{Fabrique}{l1}{This class implements a clothes factory.}
\entityintro{FabriqueFrame}{l2}{This class implements a GUI for entering the several parameters needed
 to simulate a clothes factory.}
\entityintro{Production}{l3}{This class implements the production resource.}
\entityintro{Reparation}{l4}{This class implements the reparation resource.}
\vskip .1in
\rule{\hsize}{.7mm}
\vskip .1in
\newpage
\section{Classes}{
\startsection{Class}{EvenementNouvelleMachine}{l0}{%
{\small This class implements the creation of a new machine event.}
\vskip .1in 
\startsubsubsection{Declaration}{
\fbox{\vbox{
\hbox{\vbox{\small public 
class 
EvenementNouvelleMachine}}
\noindent\hbox{\vbox{{\bf extends} simj.SimEvent}}
}}}
\startsubsubsection{Constructors}{
\vskip -2em
\begin{itemize}
\item{\vskip -1.9ex 
\membername{EvenementNouvelleMachine}
{\tt public {\bf EvenementNouvelleMachine}( {\tt double } {\bf pFiringTime} )
\label{l5}\label{l6}}%end signature
\begin{itemize}
\sld
\item{
\sld
{\bf Usage}
  \begin{itemize}\isep
   \item{
Constructs an event that creates a new machine.
}%end item
  \end{itemize}
}
\item{
\sld
{\bf Parameters}
\sld\isep
  \begin{itemize}
\sld\isep
   \item{
\sld
{\tt pFiringTime} - The firing time of this event.}
  \end{itemize}
}%end item
\end{itemize}
}%end item
\end{itemize}
}
\startsubsubsection{Methods}{
\vskip -2em
\begin{itemize}
\item{\vskip -1.9ex 
\membername{execute}
{\tt public void {\bf execute}(  )
\label{l7}\label{l8}}%end signature
\begin{itemize}
\sld
\item{
\sld
{\bf Usage}
  \begin{itemize}\isep
   \item{
Creates a new machine and sends it to the Production.
}%end item
  \end{itemize}
}
\end{itemize}
}%end item
\end{itemize}
}
\hide{inherited}{
\startsubsubsection{Methods inherited from class {\tt simj.SimEvent}}{
\par{\small 
\refdefined{l9}\vskip -2em
\begin{itemize}
\item{\vskip -1.9ex 
\membername{execute}
{\tt public abstract void {\bf execute}(  )
}%end signature
\begin{itemize}
\sld
\item{
\sld
{\bf Usage}
  \begin{itemize}\isep
   \item{
Does the actual work of this event.
 This is a primitive operation and each concrete event has to
 implement it appropriately.
}%end item
  \end{itemize}
}
\end{itemize}
}%end item
\divideents{getCurrentTime}
\item{\vskip -1.9ex 
\membername{getCurrentTime}
{\tt protected final double {\bf getCurrentTime}(  )
}%end signature
\begin{itemize}
\sld
\item{
\sld
{\bf Usage}
  \begin{itemize}\isep
   \item{
Returns the current time of the simulation.
 This commoditiy method is useful for subclasses.
}%end item
  \end{itemize}
}
\item{{\bf Returns} - 
The current time of the simulation. 
}%end item
\end{itemize}
}%end item
\divideents{getFiringTime}
\item{\vskip -1.9ex 
\membername{getFiringTime}
{\tt public double {\bf getFiringTime}(  )
}%end signature
\begin{itemize}
\sld
\item{
\sld
{\bf Usage}
  \begin{itemize}\isep
   \item{
Returns the firing or execution time of this event.
}%end item
  \end{itemize}
}
\item{{\bf Returns} - 
The firing or execution time of this event. 
}%end item
\end{itemize}
}%end item
\divideents{schedule}
\item{\vskip -1.9ex 
\membername{schedule}
{\tt protected final void {\bf schedule}( {\tt double } {\bf pFiringTime} )
}%end signature
\begin{itemize}
\sld
\item{
\sld
{\bf Usage}
  \begin{itemize}\isep
   \item{
Schedules this event at a given time. This visibility of this
 method is protected to allow subclasses to reschedule themselves
 if needed.
}%end item
  \end{itemize}
}
\item{
\sld
{\bf Parameters}
\sld\isep
  \begin{itemize}
\sld\isep
   \item{
\sld
{\tt pFiringTime} - The firing or execution time of this event.}
  \end{itemize}
}%end item
\end{itemize}
}%end item
\end{itemize}
}}
}
}
\startsection{Class}{Fabrique}{l1}{%
{\small This class implements a clothes factory. There is a production workshop
 (resouce number 1) and a reparation workshop (resource number). There are
 machines which are used in production. After some time they break down and
 are repaired by the reparation workshop. One repaired, the machines return
 in the production workshop.}
\vskip .1in 
\startsubsubsection{Declaration}{
\fbox{\vbox{
\hbox{\vbox{\small public 
class 
Fabrique}}
\noindent\hbox{\vbox{{\bf extends} simj.SimSimulation}}
}}}
\startsubsubsection{Methods}{
\vskip -2em
\begin{itemize}
\item{\vskip -1.9ex 
\membername{createEvents}
{\tt protected void {\bf createEvents}(  )
\label{l10}\label{l11}}%end signature
\begin{itemize}
\sld
\item{
\sld
{\bf Usage}
  \begin{itemize}\isep
   \item{
Implements the abstract hook method SimSimulation.createEvents
 by creating the bootstrap events of the simulation.
}%end item
  \end{itemize}
}
\end{itemize}
}%end item
\divideents{createResources}
\item{\vskip -1.9ex 
\membername{createResources}
{\tt protected void {\bf createResources}(  )
\label{l12}\label{l13}}%end signature
\begin{itemize}
\sld
\item{
\sld
{\bf Usage}
  \begin{itemize}\isep
   \item{
Implements abstract method SimSimulation.createResources
 by creating the resources of this simulation, i.e. one production
 and one reparation workshop.
}%end item
  \end{itemize}
}
\end{itemize}
}%end item
\divideents{getInstance}
\item{\vskip -1.9ex 
\membername{getInstance}
{\tt public static SimSimulation {\bf getInstance}( {\tt int } {\bf pN},
{\tt int } {\bf pM},
{\tt int } {\bf pK},
{\tt double } {\bf pMin1},
{\tt double } {\bf pMax1},
{\tt double } {\bf pMin2},
{\tt double } {\bf pMax2},
{\tt double } {\bf pP1},
{\tt double } {\bf pMPanne},
{\tt double } {\bf pFinalEventTime},
{\tt int } {\bf pScanInterval},
{\tt boolean } {\bf pFineLogging} )
\label{l14}\label{l15}}%end signature
\begin{itemize}
\sld
\item{
\sld
{\bf Usage}
  \begin{itemize}\isep
   \item{
Returns an instance of this simulation according to the provided parameters.
}%end item
  \end{itemize}
}
\item{
\sld
{\bf Parameters}
\sld\isep
  \begin{itemize}
\sld\isep
   \item{
\sld
{\tt pN} - }
   \item{
\sld
{\tt pM} - }
   \item{
\sld
{\tt pK} - }
   \item{
\sld
{\tt pMin1} - }
   \item{
\sld
{\tt pMax1} - }
   \item{
\sld
{\tt pMin2} - }
   \item{
\sld
{\tt pMax2} - }
   \item{
\sld
{\tt pP1} - }
   \item{
\sld
{\tt pMPanne} - }
   \item{
\sld
{\tt pFinalEventTime} - }
   \item{
\sld
{\tt pScanInterval} - }
   \item{
\sld
{\tt pFineLogging} - }
  \end{itemize}
}%end item
\item{{\bf Returns} - 
 
}%end item
\end{itemize}
}%end item
\divideents{getProduction}
\item{\vskip -1.9ex 
\membername{getProduction}
{\tt public Production {\bf getProduction}(  )
\label{l16}\label{l17}}%end signature
\begin{itemize}
\sld
\item{
\sld
{\bf Usage}
  \begin{itemize}\isep
   \item{
Returns the production resource.
}%end item
  \end{itemize}
}
\item{{\bf Returns} - 
The resource Production. 
}%end item
\end{itemize}
}%end item
\divideents{getReparation}
\item{\vskip -1.9ex 
\membername{getReparation}
{\tt public Reparation {\bf getReparation}(  )
\label{l18}\label{l19}}%end signature
\begin{itemize}
\sld
\item{
\sld
{\bf Usage}
  \begin{itemize}\isep
   \item{
Return the reparation resource.
}%end item
  \end{itemize}
}
\item{{\bf Returns} - 
The resource Reparation. 
}%end item
\end{itemize}
}%end item
\end{itemize}
}
\hide{inherited}{
\startsubsubsection{Methods inherited from class {\tt simj.SimSimulation}}{
\par{\small 
\refdefined{l20}\vskip -2em
\begin{itemize}
\item{\vskip -1.9ex 
\membername{createEvents}
{\tt protected abstract void {\bf createEvents}(  )
}%end signature
\begin{itemize}
\sld
\item{
\sld
{\bf Usage}
  \begin{itemize}\isep
   \item{
Creates the bootstrapping events of the simulation.
 This is a primitive operation and has to be implemented by subclasses.
}%end item
  \end{itemize}
}
\end{itemize}
}%end item
\divideents{createResources}
\item{\vskip -1.9ex 
\membername{createResources}
{\tt protected abstract void {\bf createResources}(  )
}%end signature
\begin{itemize}
\sld
\item{
\sld
{\bf Usage}
  \begin{itemize}\isep
   \item{
Creates the several resources of the simulation.
 This is a primitive operation and has to be implemented by subclasses.
}%end item
  \end{itemize}
}
\end{itemize}
}%end item
\divideents{getInstance}
\item{\vskip -1.9ex 
\membername{getInstance}
{\tt public static SimSimulation {\bf getInstance}(  )
}%end signature
\begin{itemize}
\sld
\item{
\sld
{\bf Usage}
  \begin{itemize}\isep
   \item{
Returns the unique instance of this singleton class.
}%end item
  \end{itemize}
}
\item{{\bf Returns} - 
The unique instance of this singleton class. 
}%end item
\end{itemize}
}%end item
\divideents{getNumberOfResources}
\item{\vskip -1.9ex 
\membername{getNumberOfResources}
{\tt public int {\bf getNumberOfResources}(  )
}%end signature
\begin{itemize}
\sld
\item{
\sld
{\bf Usage}
  \begin{itemize}\isep
   \item{
Returns the number of resources of the simulation.
}%end item
  \end{itemize}
}
\item{{\bf Returns} - 
The number of resources of the simulation. 
}%end item
\end{itemize}
}%end item
\divideents{getResource}
\item{\vskip -1.9ex 
\membername{getResource}
{\tt public SimResource {\bf getResource}( {\tt int } {\bf index} )
}%end signature
\begin{itemize}
\sld
\item{
\sld
{\bf Usage}
  \begin{itemize}\isep
   \item{
Returns the resource at the specified index.
}%end item
  \end{itemize}
}
\item{
\sld
{\bf Parameters}
\sld\isep
  \begin{itemize}
\sld\isep
   \item{
\sld
{\tt index} - An index into the resources of this simulation
 (between {\tt 1} and {\tt getNumberOfResources}).}
  \end{itemize}
}%end item
\item{{\bf Returns} - 
The resource at the specified index. 
}%end item
\end{itemize}
}%end item
\divideents{registerResource}
\item{\vskip -1.9ex 
\membername{registerResource}
{\tt  void {\bf registerResource}( {\tt simj.SimResource } {\bf pRes} )
}%end signature
\begin{itemize}
\sld
\item{
\sld
{\bf Usage}
  \begin{itemize}\isep
   \item{
Adds a resource to this simulation.
}%end item
  \end{itemize}
}
\item{
\sld
{\bf Parameters}
\sld\isep
  \begin{itemize}
\sld\isep
   \item{
\sld
{\tt pRes} - The resource to add to this simulation.}
  \end{itemize}
}%end item
\end{itemize}
}%end item
\divideents{setupSimulation}
\item{\vskip -1.9ex 
\membername{setupSimulation}
{\tt protected void {\bf setupSimulation}(  )
}%end signature
\begin{itemize}
\sld
\item{
\sld
{\bf Usage}
  \begin{itemize}\isep
   \item{
Does some additional simulation initialization configuration.
 This is a hook operation and may be overridden by subclasses.
 By default it does nothing.
}%end item
  \end{itemize}
}
\end{itemize}
}%end item
\divideents{startSimulation}
\item{\vskip -1.9ex 
\membername{startSimulation}
{\tt public final void {\bf startSimulation}(  )
}%end signature
\begin{itemize}
\sld
\item{
\sld
{\bf Usage}
  \begin{itemize}\isep
   \item{
Initializes and starts the simulation.
 This is a template method and calls several primitive and hook operations.
}%end item
  \end{itemize}
}
\end{itemize}
}%end item
\end{itemize}
}}
}
}
\startsection{Class}{FabriqueFrame}{l2}{%
{\small This class implements a GUI for entering the several parameters needed
 to simulate a clothes factory.}
\vskip .1in 
\startsubsubsection{Declaration}{
\fbox{\vbox{
\hbox{\vbox{\small public 
class 
FabriqueFrame}}
\noindent\hbox{\vbox{{\bf extends} javax.swing.JFrame}}
}}}
\startsubsubsection{Serializable Fields}{
\begin{itemize}
\item{
private JCheckBox fineLogging\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JLabel dureeLabel\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JTextField dureeSimulation\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JPanel jPanel1\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JTextField machineReserve\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JTextField machineService\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JLabel machinesReserveLabel\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JLabel machinesServiceLabel\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JTextField mecaniciensService\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JLabel mecaniciensServiceLabel\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JTextField moyPannes\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JLabel moyPannesLabel\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JTextField probPanne\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JLabel probPanneLabel\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JTextField scanInterval\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JLabel scanIntervalLabel\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JButton startButton\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JTextField tempsRepMaxGrave\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JLabel tempsRepMaxGraveLabel\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JTextField tempsRepMaxLegere\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JLabel tempsRepMaxLegereLabel\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JTextField tempsRepMinGrave\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JLabel tempsRepMinGraveLabel\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JTextField tempsRepMinLegere\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JLabel tempsRepMinLegereLabel\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\item{
private JLabel titleLabel\begin{itemize}\item{\vskip -.9ex }\end{itemize}
}
\end{itemize}
}
\startsubsubsection{Constructors}{
\vskip -2em
\begin{itemize}
\item{\vskip -1.9ex 
\membername{FabriqueFrame}
{\tt public {\bf FabriqueFrame}(  )
\label{l21}\label{l22}}%end signature
\begin{itemize}
\sld
\item{
\sld
{\bf Usage}
  \begin{itemize}\isep
   \item{
Creates new form SupermarcheFrame.
}%end item
  \end{itemize}
}
\end{itemize}
}%end item
\end{itemize}
}
\startsubsubsection{Methods}{
\vskip -2em
\begin{itemize}
\item{\vskip -1.9ex 
\membername{main}
{\tt public static void {\bf main}( {\tt java.lang.String []} {\bf args} )
\label{l23}\label{l24}}%end signature
\begin{itemize}
\sld
\item{
\sld
{\bf Usage}
  \begin{itemize}\isep
   \item{
The main method of this class: it displays the GUI for the factory
 simulation parametrization and creation.
}%end item
  \end{itemize}
}
\item{
\sld
{\bf Parameters}
\sld\isep
  \begin{itemize}
\sld\isep
   \item{
\sld
{\tt args} - A string array with the command line arguments (here they
 are not used).}
  \end{itemize}
}%end item
\end{itemize}
}%end item
\end{itemize}
}
\hide{inherited}{
\startsubsubsection{Methods inherited from class {\tt javax.swing.JFrame}}{
\par{\small 
\refdefined{l25}\vskip -2em
\begin{itemize}
\item{\vskip -1.9ex 
\membername{\textless clinit\textgreater }
{\tt static void {\bf \textless clinit\textgreater }(  )
}%end signature
}%end item
\divideents{addImpl}
\item{\vskip -1.9ex 
\membername{addImpl}
{\tt protected void {\bf addImpl}( {\tt java.awt.Component } {\bf arg0},
{\tt java.lang.Object } {\bf arg1},
{\tt int } {\bf arg2} )
}%end signature
}%end item
\divideents{createRootPane}
\item{\vskip -1.9ex 
\membername{createRootPane}
{\tt protected JRootPane {\bf createRootPane}(  )
}%end signature
}%end item
\divideents{frameInit}
\item{\vskip -1.9ex 
\membername{frameInit}
{\tt protected void {\bf frameInit}(  )
}%end signature
}%end item
\divideents{getAccessibleContext}
\item{\vskip -1.9ex 
\membername{getAccessibleContext}
{\tt public AccessibleContext {\bf getAccessibleContext}(  )
}%end signature
}%end item
\divideents{getContentPane}
\item{\vskip -1.9ex 
\membername{getContentPane}
{\tt public Container {\bf getContentPane}(  )
}%end signature
}%end item
\divideents{getDefaultCloseOperation}
\item{\vskip -1.9ex 
\membername{getDefaultCloseOperation}
{\tt public int {\bf getDefaultCloseOperation}(  )
}%end signature
}%end item
\divideents{getGlassPane}
\item{\vskip -1.9ex 
\membername{getGlassPane}
{\tt public Component {\bf getGlassPane}(  )
}%end signature
}%end item
\divideents{getGraphics}
\item{\vskip -1.9ex 
\membername{getGraphics}
{\tt public Graphics {\bf getGraphics}(  )
}%end signature
}%end item
\divideents{getJMenuBar}
\item{\vskip -1.9ex 
\membername{getJMenuBar}
{\tt public JMenuBar {\bf getJMenuBar}(  )
}%end signature
}%end item
\divideents{getLayeredPane}
\item{\vskip -1.9ex 
\membername{getLayeredPane}
{\tt public JLayeredPane {\bf getLayeredPane}(  )
}%end signature
}%end item
\divideents{getRootPane}
\item{\vskip -1.9ex 
\membername{getRootPane}
{\tt public JRootPane {\bf getRootPane}(  )
}%end signature
}%end item
\divideents{getTransferHandler}
\item{\vskip -1.9ex 
\membername{getTransferHandler}
{\tt public TransferHandler {\bf getTransferHandler}(  )
}%end signature
}%end item
\divideents{isDefaultLookAndFeelDecorated}
\item{\vskip -1.9ex 
\membername{isDefaultLookAndFeelDecorated}
{\tt public static boolean {\bf isDefaultLookAndFeelDecorated}(  )
}%end signature
}%end item
\divideents{isRootPaneCheckingEnabled}
\item{\vskip -1.9ex 
\membername{isRootPaneCheckingEnabled}
{\tt protected boolean {\bf isRootPaneCheckingEnabled}(  )
}%end signature
}%end item
\divideents{paramString}
\item{\vskip -1.9ex 
\membername{paramString}
{\tt protected String {\bf paramString}(  )
}%end signature
}%end item
\divideents{processWindowEvent}
\item{\vskip -1.9ex 
\membername{processWindowEvent}
{\tt protected void {\bf processWindowEvent}( {\tt java.awt.event.WindowEvent } {\bf arg0} )
}%end signature
}%end item
\divideents{remove}
\item{\vskip -1.9ex 
\membername{remove}
{\tt public void {\bf remove}( {\tt java.awt.Component } {\bf arg0} )
}%end signature
}%end item
\divideents{repaint}
\item{\vskip -1.9ex 
\membername{repaint}
{\tt public void {\bf repaint}( {\tt long } {\bf arg0},
{\tt int } {\bf arg1},
{\tt int } {\bf arg2},
{\tt int } {\bf arg3},
{\tt int } {\bf arg4} )
}%end signature
}%end item
\divideents{setContentPane}
\item{\vskip -1.9ex 
\membername{setContentPane}
{\tt public void {\bf setContentPane}( {\tt java.awt.Container } {\bf arg0} )
}%end signature
}%end item
\divideents{setDefaultCloseOperation}
\item{\vskip -1.9ex 
\membername{setDefaultCloseOperation}
{\tt public void {\bf setDefaultCloseOperation}( {\tt int } {\bf arg0} )
}%end signature
}%end item
\divideents{setDefaultLookAndFeelDecorated}
\item{\vskip -1.9ex 
\membername{setDefaultLookAndFeelDecorated}
{\tt public static void {\bf setDefaultLookAndFeelDecorated}( {\tt boolean } {\bf arg0} )
}%end signature
}%end item
\divideents{setGlassPane}
\item{\vskip -1.9ex 
\membername{setGlassPane}
{\tt public void {\bf setGlassPane}( {\tt java.awt.Component } {\bf arg0} )
}%end signature
}%end item
\divideents{setIconImage}
\item{\vskip -1.9ex 
\membername{setIconImage}
{\tt public void {\bf setIconImage}( {\tt java.awt.Image } {\bf arg0} )
}%end signature
}%end item
\divideents{setJMenuBar}
\item{\vskip -1.9ex 
\membername{setJMenuBar}
{\tt public void {\bf setJMenuBar}( {\tt javax.swing.JMenuBar } {\bf arg0} )
}%end signature
}%end item
\divideents{setLayeredPane}
\item{\vskip -1.9ex 
\membername{setLayeredPane}
{\tt public void {\bf setLayeredPane}( {\tt javax.swing.JLayeredPane } {\bf arg0} )
}%end signature
}%end item
\divideents{setLayout}
\item{\vskip -1.9ex 
\membername{setLayout}
{\tt public void {\bf setLayout}( {\tt java.awt.LayoutManager } {\bf arg0} )
}%end signature
}%end item
\divideents{setRootPane}
\item{\vskip -1.9ex 
\membername{setRootPane}
{\tt protected void {\bf setRootPane}( {\tt javax.swing.JRootPane } {\bf arg0} )
}%end signature
}%end item
\divideents{setRootPaneCheckingEnabled}
\item{\vskip -1.9ex 
\membername{setRootPaneCheckingEnabled}
{\tt protected void {\bf setRootPaneCheckingEnabled}( {\tt boolean } {\bf arg0} )
}%end signature
}%end item
\divideents{setTransferHandler}
\item{\vskip -1.9ex 
\membername{setTransferHandler}
{\tt public void {\bf setTransferHandler}( {\tt javax.swing.TransferHandler } {\bf arg0} )
}%end signature
}%end item
\divideents{update}
\item{\vskip -1.9ex 
\membername{update}
{\tt public void {\bf update}( {\tt java.awt.Graphics } {\bf arg0} )
}%end signature
}%end item
\end{itemize}
}}
\startsubsubsection{Methods inherited from class {\tt java.awt.Frame}}{
\par{\small 
\refdefined{l26}\vskip -2em
\begin{itemize}
\item{\vskip -1.9ex 
\membername{\textless clinit\textgreater }
{\tt static void {\bf \textless clinit\textgreater }(  )
}%end signature
}%end item
\divideents{addNotify}
\item{\vskip -1.9ex 
\membername{addNotify}
{\tt public void {\bf addNotify}(  )
}%end signature
}%end item
\divideents{constructComponentName}
\item{\vskip -1.9ex 
\membername{constructComponentName}
{\tt  String {\bf constructComponentName}(  )
}%end signature
}%end item
\divideents{getAccessibleContext}
\item{\vskip -1.9ex 
\membername{getAccessibleContext}
{\tt public AccessibleContext {\bf getAccessibleContext}(  )
}%end signature
}%end item
\divideents{getCursorType}
\item{\vskip -1.9ex 
\membername{getCursorType}
{\tt public int {\bf getCursorType}(  )
}%end signature
}%end item
\divideents{getExtendedState}
\item{\vskip -1.9ex 
\membername{getExtendedState}
{\tt public int {\bf getExtendedState}(  )
}%end signature
}%end item
\divideents{getFrames}
\item{\vskip -1.9ex 
\membername{getFrames}
{\tt public static Frame {\bf getFrames}(  )
}%end signature
}%end item
\divideents{getIconImage}
\item{\vskip -1.9ex 
\membername{getIconImage}
{\tt public Image {\bf getIconImage}(  )
}%end signature
}%end item
\divideents{getMaximizedBounds}
\item{\vskip -1.9ex 
\membername{getMaximizedBounds}
{\tt public Rectangle {\bf getMaximizedBounds}(  )
}%end signature
}%end item
\divideents{getMenuBar}
\item{\vskip -1.9ex 
\membername{getMenuBar}
{\tt public MenuBar {\bf getMenuBar}(  )
}%end signature
}%end item
\divideents{getState}
\item{\vskip -1.9ex 
\membername{getState}
{\tt public synchronized int {\bf getState}(  )
}%end signature
}%end item
\divideents{getTitle}
\item{\vskip -1.9ex 
\membername{getTitle}
{\tt public String {\bf getTitle}(  )
}%end signature
}%end item
\divideents{isResizable}
\item{\vskip -1.9ex 
\membername{isResizable}
{\tt public boolean {\bf isResizable}(  )
}%end signature
}%end item
\divideents{isUndecorated}
\item{\vskip -1.9ex 
\membername{isUndecorated}
{\tt public boolean {\bf isUndecorated}(  )
}%end signature
}%end item
\divideents{paramString}
\item{\vskip -1.9ex 
\membername{paramString}
{\tt protected String {\bf paramString}(  )
}%end signature
}%end item
\divideents{postProcessKeyEvent}
\item{\vskip -1.9ex 
\membername{postProcessKeyEvent}
{\tt  void {\bf postProcessKeyEvent}( {\tt java.awt.event.KeyEvent } {\bf arg0} )
}%end signature
}%end item
\divideents{remove}
\item{\vskip -1.9ex 
\membername{remove}
{\tt public void {\bf remove}( {\tt java.awt.MenuComponent } {\bf arg0} )
}%end signature
}%end item
\divideents{removeNotify}
\item{\vskip -1.9ex 
\membername{removeNotify}
{\tt public void {\bf removeNotify}(  )
}%end signature
}%end item
\divideents{setBackground}
\item{\vskip -1.9ex 
\membername{setBackground}
{\tt public void {\bf setBackground}( {\tt java.awt.Color } {\bf arg0} )
}%end signature
}%end item
\divideents{setCursor}
\item{\vskip -1.9ex 
\membername{setCursor}
{\tt public void {\bf setCursor}( {\tt int } {\bf arg0} )
}%end signature
}%end item
\divideents{setExtendedState}
\item{\vskip -1.9ex 
\membername{setExtendedState}
{\tt public void {\bf setExtendedState}( {\tt int } {\bf arg0} )
}%end signature
}%end item
\divideents{setIconImage}
\item{\vskip -1.9ex 
\membername{setIconImage}
{\tt public void {\bf setIconImage}( {\tt java.awt.Image } {\bf arg0} )
}%end signature
}%end item
\divideents{setMaximizedBounds}
\item{\vskip -1.9ex 
\membername{setMaximizedBounds}
{\tt public void {\bf setMaximizedBounds}( {\tt java.awt.Rectangle } {\bf arg0} )
}%end signature
}%end item
\divideents{setMenuBar}
\item{\vskip -1.9ex 
\membername{setMenuBar}
{\tt public void {\bf setMenuBar}( {\tt java.awt.MenuBar } {\bf arg0} )
}%end signature
}%end item
\divideents{setOpacity}
\item{\vskip -1.9ex 
\membername{setOpacity}
{\tt public void {\bf setOpacity}( {\tt float } {\bf arg0} )
}%end signature
}%end item
\divideents{setResizable}
\item{\vskip -1.9ex 
\membername{setResizable}
{\tt public void {\bf setResizable}( {\tt boolean } {\bf arg0} )
}%end signature
}%end item
\divideents{setShape}
\item{\vskip -1.9ex 
\membername{setShape}
{\tt public void {\bf setShape}( {\tt java.awt.Shape } {\bf arg0} )
}%end signature
}%end item
\divideents{setState}
\item{\vskip -1.9ex 
\membername{setState}
{\tt public synchronized void {\bf setState}( {\tt int } {\bf arg0} )
}%end signature
}%end item
\divideents{setTitle}
\item{\vskip -1.9ex 
\membername{setTitle}
{\tt public void {\bf setTitle}( {\tt java.lang.String } {\bf arg0} )
}%end signature
}%end item
\divideents{setUndecorated}
\item{\vskip -1.9ex 
\membername{setUndecorated}
{\tt public void {\bf setUndecorated}( {\tt boolean } {\bf arg0} )
}%end signature
}%end item
\end{itemize}
}}
\startsubsubsection{Methods inherited from class {\tt java.awt.Window}}{
\par{\small 
\refdefined{l27}\vskip -2em
\begin{itemize}
\item{\vskip -1.9ex 
\membername{\textless clinit\textgreater }
{\tt static void {\bf \textless clinit\textgreater }(  )
}%end signature
}%end item
\divideents{addNotify}
\item{\vskip -1.9ex 
\membername{addNotify}
{\tt public void {\bf addNotify}(  )
}%end signature
}%end item
\divideents{addOwnedWindow}
\item{\vskip -1.9ex 
\membername{addOwnedWindow}
{\tt  void {\bf addOwnedWindow}( {\tt java.lang.ref.WeakReference } {\bf arg0} )
}%end signature
}%end item
\divideents{addPropertyChangeListener}
\item{\vskip -1.9ex 
\membername{addPropertyChangeListener}
{\tt public void {\bf addPropertyChangeListener}( {\tt java.beans.PropertyChangeListener } {\bf arg0} )
}%end signature
}%end item
\divideents{addPropertyChangeListener}
\item{\vskip -1.9ex 
\membername{addPropertyChangeListener}
{\tt public void {\bf addPropertyChangeListener}( {\tt java.lang.String } {\bf arg0},
{\tt java.beans.PropertyChangeListener } {\bf arg1} )
}%end signature
}%end item
\divideents{addWindowFocusListener}
\item{\vskip -1.9ex 
\membername{addWindowFocusListener}
{\tt public synchronized void {\bf addWindowFocusListener}( {\tt java.awt.event.WindowFocusListener } {\bf arg0} )
}%end signature
}%end item
\divideents{addWindowListener}
\item{\vskip -1.9ex 
\membername{addWindowListener}
{\tt public synchronized void {\bf addWindowListener}( {\tt java.awt.event.WindowListener } {\bf arg0} )
}%end signature
}%end item
\divideents{addWindowStateListener}
\item{\vskip -1.9ex 
\membername{addWindowStateListener}
{\tt public synchronized void {\bf addWindowStateListener}( {\tt java.awt.event.WindowStateListener } {\bf arg0} )
}%end signature
}%end item
\divideents{adjustDecendantsOnParent}
\item{\vskip -1.9ex 
\membername{adjustDecendantsOnParent}
{\tt  void {\bf adjustDecendantsOnParent}( {\tt int } {\bf arg0} )
}%end signature
}%end item
\divideents{adjustListeningChildrenOnParent}
\item{\vskip -1.9ex 
\membername{adjustListeningChildrenOnParent}
{\tt  void {\bf adjustListeningChildrenOnParent}( {\tt long } {\bf arg0},
{\tt int } {\bf arg1} )
}%end signature
}%end item
\divideents{applyCompoundShape}
\item{\vskip -1.9ex 
\membername{applyCompoundShape}
{\tt final void {\bf applyCompoundShape}( {\tt sun.java2d.pipe.Region } {\bf arg0} )
}%end signature
}%end item
\divideents{applyCurrentShape}
\item{\vskip -1.9ex 
\membername{applyCurrentShape}
{\tt final void {\bf applyCurrentShape}(  )
}%end signature
}%end item
\divideents{applyResourceBundle}
\item{\vskip -1.9ex 
\membername{applyResourceBundle}
{\tt public void {\bf applyResourceBundle}( {\tt java.util.ResourceBundle } {\bf arg0} )
}%end signature
}%end item
\divideents{applyResourceBundle}
\item{\vskip -1.9ex 
\membername{applyResourceBundle}
{\tt public void {\bf applyResourceBundle}( {\tt java.lang.String } {\bf arg0} )
}%end signature
}%end item
\divideents{canContainFocusOwner}
\item{\vskip -1.9ex 
\membername{canContainFocusOwner}
{\tt  boolean {\bf canContainFocusOwner}( {\tt java.awt.Component } {\bf arg0} )
}%end signature
}%end item
\divideents{clearMostRecentFocusOwnerOnHide}
\item{\vskip -1.9ex 
\membername{clearMostRecentFocusOwnerOnHide}
{\tt final void {\bf clearMostRecentFocusOwnerOnHide}(  )
}%end signature
}%end item
\divideents{closeSplashScreen}
\item{\vskip -1.9ex 
\membername{closeSplashScreen}
{\tt final void {\bf closeSplashScreen}(  )
}%end signature
}%end item
\divideents{connectOwnedWindow}
\item{\vskip -1.9ex 
\membername{connectOwnedWindow}
{\tt  void {\bf connectOwnedWindow}( {\tt java.awt.Window } {\bf arg0} )
}%end signature
}%end item
\divideents{constructComponentName}
\item{\vskip -1.9ex 
\membername{constructComponentName}
{\tt  String {\bf constructComponentName}(  )
}%end signature
}%end item
\divideents{createBufferStrategy}
\item{\vskip -1.9ex 
\membername{createBufferStrategy}
{\tt public void {\bf createBufferStrategy}( {\tt int } {\bf arg0} )
}%end signature
}%end item
\divideents{createBufferStrategy}
\item{\vskip -1.9ex 
\membername{createBufferStrategy}
{\tt public void {\bf createBufferStrategy}( {\tt int } {\bf arg0},
{\tt java.awt.BufferCapabilities } {\bf arg1} )
}%end signature
}%end item
\divideents{deliverMouseWheelToAncestor}
\item{\vskip -1.9ex 
\membername{deliverMouseWheelToAncestor}
{\tt  void {\bf deliverMouseWheelToAncestor}( {\tt java.awt.event.MouseWheelEvent } {\bf arg0} )
}%end signature
}%end item
\divideents{dispatchEventImpl}
\item{\vskip -1.9ex 
\membername{dispatchEventImpl}
{\tt  void {\bf dispatchEventImpl}( {\tt java.awt.AWTEvent } {\bf arg0} )
}%end signature
}%end item
\divideents{dispatchMouseWheelToAncestor}
\item{\vskip -1.9ex 
\membername{dispatchMouseWheelToAncestor}
{\tt  boolean {\bf dispatchMouseWheelToAncestor}( {\tt java.awt.event.MouseWheelEvent } {\bf arg0} )
}%end signature
}%end item
\divideents{dispose}
\item{\vskip -1.9ex 
\membername{dispose}
{\tt public void {\bf dispose}(  )
}%end signature
}%end item
\divideents{disposeImpl}
\item{\vskip -1.9ex 
\membername{disposeImpl}
{\tt  void {\bf disposeImpl}(  )
}%end signature
}%end item
\divideents{doDispose}
\item{\vskip -1.9ex 
\membername{doDispose}
{\tt  void {\bf doDispose}(  )
}%end signature
}%end item
\divideents{eventEnabled}
\item{\vskip -1.9ex 
\membername{eventEnabled}
{\tt  boolean {\bf eventEnabled}( {\tt java.awt.AWTEvent } {\bf arg0} )
}%end signature
}